Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus

### 2017-11-28 paper.tex
djfkdj
dfjk

\begin{table}[]
\centering
\caption{PSMs Within 1\% FDR Before and After Calibration}
\label{tbl:calib}
\begin{tabular}{lll}

                                                                                      & Orig        & Calib        \\
 PSM Count                                                           &      270548   &   273825        \\
 Average Error (ppm)                                                              &      -2.08      &        -0.10      \\
 St. Dev of Error                                                    &       2.24      &        1.06      \\
\end{tabular}
\end{table}

@@

\newpage

@@

\begin{figure}[H]
\includegraphics{fig3-searchTypes.png}
\caption{The three searches illustrated. Blue regions signify the allowed mass differences, while the pink ones show the mass differences that are not considered.}
\label{fig:fig3-searchTypes}
\end{figure}

>>>>

\begin{table}[]
\centering
\caption{PSMs Within 1\% FDR Before and After Calibration}
\label{tbl:calib}
\begin{tabular}{lll}
                                                                                      & Orig        & Calib        \\
 PSM Count                                                           &      270548   &   273825        \\
 Average Error (ppm)                                                              &      -2.08      &        -0.10      \\
 St. Dev of Error                                                    &       2.24      &        1.06      \\
\end{tabular}
\end{table}

@@

@@

\begin{figure}[H]
\includegraphics{fig3-searchTypes.png}
\caption{Schematic illustration of the three search types. Certain mass differences between the observed experimental mass and theoretical candidate masses are allowed (blue regions) or not considered (pink regions).}
\label{fig:fig3-searchTypes}
\end{figure}
